Andres Karjus

### 2018-07-05 index.Rmd
writing centre info added
bib for new paper

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
* Andres Karjus, Martin Ehala, [accepted]. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change.
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

@@

- I have been developing materials on data visualization using R; these have been used during 2017-2018 in a number of different workshops for humanities and social science audiences, collectively under the name of _aRt of the Figure_ (all the materials and code available [here](https://andreskarjus.github.io/artofthefigure/)).
- One outlet for these has been through the PPLS Writing Centre - the dates and booking information are available [here](http://writingcentre.ppls.ed.ac.uk/workshops/). During the semester it's a 1-hour workshop, extended to 2 hours for the extracurricular summer edition.
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page -> Book an appointment -> look for my name in the list of tutors in the 'Select staff' dropdown menu.
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).

>>>>

* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | <a href="karjus_quantifying_2018.bib" target="_blank">bib</a> | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
* Andres Karjus, Martin Ehala, [accepted]. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change.
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

@@

- I have been developing materials on data visualization using R; these have been used during 2017-2018 in a number of different workshops for humanities and social science audiences, collectively under the name of _aRt of the Figure_ (all the materials and code available [here](https://andreskarjus.github.io/artofthefigure/)).
- One outlet for these has been through the PPLS Writing Centre - the dates and booking information are available [here](http://writingcentre.ppls.ed.ac.uk/workshops/). During the semester it's a 1-hour workshop, extended to 2 hours for the extracurricular summer edition.
- [I am available for booking](http://writingcentre.ppls.ed.ac.uk/appointments/) year around as a written communication consultant via the Edinburgh University School of Psychology, Philosophy and Language Sciences Writing Centre - specializing in writing about and presenting (graphs and figures of) data and data analysis results. This service is available to students of the School only. To book, go to the [appointments](http://writingcentre.ppls.ed.ac.uk/appointments/) page -> Book an appointment -> look for my name in the list of tutors in the 'Select staff' dropdown menu.
- In the summer of 2018, I am working with the PPLS Writing Centre to provide a drop-in quantitative research help service for PPLS MSc students working on their theses, [see here for dates and details](https://writingcentre.ppls.ed.ac.uk/2018/06/18/drop-in-quantitative-research-help/).
- I am also engaged in teaching stats and R to [Edinburgh Uni psychology](https://www.ed.ac.uk/ppls/psychology) masters students (since 2017).
